### 2024-02-15 paper_sisc_first_revision/localpsf.tex
added color to frog negative impulse pictures

One limitation of our method is that not all data misfit Hessians satisfy the local non-negative integral kernel properties. We note, in particular, that the wave inverse problem data misfit Hessian has a substantial proportion of negative entries in its integral kernel. In this case more specialized techniques based on pseudodifferential operator theory have been developed, e.g., \cite{DemanetEtAl12,HerrmannMoghaddamStolk08,Symes08}. However, many data misfit Hessians of practical interest do satisfy the local non-negative integral kernel properties (either exactly or approximately), and the proposed method is targeted at approximating these Hessians.

>>>>

One limitation of our method is that not all data misfit Hessians satisfy the local non-negative integral kernel properties. We note, in particular, that the wave inverse problem data misfit Hessian and Gauss-Newton Hessian have a substantial proportion of negative entries in their integral kernels. In this case more specialized techniques based on pseudodifferential operator theory have been developed, e.g., \cite{DemanetEtAl12,HerrmannMoghaddamStolk08,Symes08}. However, many data misfit Hessians of practical interest do satisfy the local non-negative integral kernel properties (either exactly or approximately), and the proposed method is targeted at approximating these Hessians.
